CF Registry Analysis

### 2025-03-03 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
updated plots for Christine

```{r}
t1 <- era1 %>% tbl_regression(exponentiate = T)
t1
ggcoef_model(era1,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
t2 <- era2 %>% tbl_regression(exponentiate = T)
t2
ggcoef_model(era2,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
t3 <- era3 %>% tbl_regression(exponentiate = T)
t3
ggcoef_model(era3,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
```

@@

```{r}
tbl_merge(
  tbls = list(t1, t2, t3),
  tab_spanner = c("2003 - 2008", "2009 - 2013", "2014 - 2018")
)
comb_plot <- ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
comb_plot
ggsave("./Dissemination/Figures/time_combined_forest.png",
  plot = comb_plot, width = 12, height = 9, units = "in"
)
```

>>>>

```{r}
t1 <- era1 %>% tbl_regression(exponentiate = T)
t1
ggcoef_model(era1,
  show_p_values = F, add_reference_rows = T, exponentiate = T, shape_guide = F,
  signif_stars = F, colour = "significance", shape = "reference_row",
  shape_values = c(16, 15)
)
```

@@

```{r}
t2 <- era2 %>% tbl_regression(exponentiate = T)
t2
ggcoef_model(era2,
  show_p_values = F, add_reference_rows = T, exponentiate = T, shape_guide = F,
  signif_stars = F, colour = "significance", shape = "reference_row",
  shape_values = c(16, 15)
)
```

@@

```{r}
t3 <- era3 %>% tbl_regression(exponentiate = T)
t3
ggcoef_model(era3,
  show_p_values = F, add_reference_rows = T, exponentiate = T, shape_guide = F,
  signif_stars = F, colour = "significance", shape = "reference_row",
  shape_values = c(16, 15)
)
```

@@

```{r}
tbl_merge(
  tbls = list(t1, t2, t3),
  tab_spanner = c("2003 - 2008", "2009 - 2013", "2014 - 2018")
)
comb_plot <- ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, shape_guide = F,
  colour = "significance", shape = "reference_row", shape_values = c(16, 15),
  type = "faceted"
)
comb_plot
ggsave("./Dissemination/Figures/time_combined_forest.png",
  plot = comb_plot, width = 12, height = 9, units = "in"
)
```
